Market simulator

### 2020-10-08 analysis/05_market_simulator.Rmd
fixed formating error

```{r organization-reactive-table}
# Assign level labels
org_table <- data.frame(
  levels = c(
    # Organization
    "Amnesty International",
    "Greenpeace", 
    "Oxfam", 
    "Red Cross",
    # Issue area
    "Environment", 
    "Human rights",
    "Refugee relief",
    # Financial transparency
    "Engages in financial transparency",
    # Financial accountability
    "Engages in financial accountability",
    # Funding sources
    "Handful of wealthy private donors", 
    "Government grants",
    # Relationship with host government
    "Criticized by government",
    "Under government crackdown"
  )
)

>>>>

```{r organization-reactive-table}

# Placeholder for organization reactive table
org_table <- as.data.frame(matrix(0, nrow = nrow(organization_data)))
# org_table <- reactive({read.csv(input$file_org$datapath)})

# Assign level labels
org_table <- data.frame(
  levels = c(
    # Organization
    "Amnesty International",
    "Greenpeace", 
    "Oxfam", 
    "Red Cross",
    # Issue area
    "Environment", 
    "Human rights",
    "Refugee relief",
    # Financial transparency
    "Engages in financial transparency",
    # Financial accountability
    "Engages in financial accountability",
    # Funding sources
    "Handful of wealthy private donors", 
    "Government grants",
    # Relationship with host government
    "Criticized by government",
    "Under government crackdown"
  )
)

# I think what we need to do to import data to fill this reactive element we need it look something like this

# org_table$org1_value[where (input$file_org == 1) and the corresponding level matches %in% org_table$levels] <- 1
